A \proglang{Python}/\proglang{Zig} optimized and customizable implementation for the $\rho_{DCCA}$ and $DMC_x^2$

### 2025-04-08 paper_v02/article.tex
12 series paper description

With that configuration, the results are very simmilar, except that the \pkg{Zebende} pure \proglang{Python} implementation ended in the third position, performing better than the \pkg{DCCA-Python} (4th) and the \pkg{DCCA-R-Java} (5th) packages.

>>>>

With that configuration, the optimized \proglang{Zig} version still the fastest, followed by the basic \proglang{Zig} implementation. The \pkg{Zebende} pure \proglang{Python} implementation ended in the third position, performing better than the \pkg{DCCA-Python} (4th) and the \pkg{DCCA-R-Java} (5th) packages. The lists ended with the \pkg{DFA} in the 6th position.
